humanCdGF_entero_predict

### 2016-09-02 code/HumanCdGF_entero_predict.Rmd
added enterotype files to rmd

# read in files
meta_file   <- read.table('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF_metadata.txt', sep = '\t',
                        header = T)
shared_file <- read.table('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF.an.unique_list.0.03.subsample.shared',
                          sep='\t',header = T, row.names = 'Group')
tax_file <- read.table('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/mothur/gf_cdiff.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.an.unique_list.0.03.cons.taxonomy',
                       sep='\t',header = T, row.names = 'OTU')
# function to label otu with tax
source('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/code/tax_level.R')

@@

# create enterotypes
# first generate distance matrices
dist.JSD <- function(inMatrix, pseudocount=0.000001, ...) {
	KLD <- function(x,y) sum(x *log(x/y))
	JSD<- function(x,y) sqrt(0.5 * KLD(x, (x+y)/2) + 0.5 * KLD(y, (x+y)/2))
	matrixColSize <- length(colnames(inMatrix))
	matrixRowSize <- length(rownames(inMatrix))
	colnames <- colnames(inMatrix)
	resultsMatrix <- matrix(0, matrixColSize, matrixColSize)

  inMatrix = apply(inMatrix,1:2,function(x) ifelse (x==0,pseudocount,x))

	for(i in 1:matrixColSize) {
		for(j in 1:matrixColSize) { 
			resultsMatrix[i,j]=JSD(as.vector(inMatrix[,i]),
			as.vector(inMatrix[,j]))
		}
	}
	colnames -> colnames(resultsMatrix) -> rownames(resultsMatrix)
	as.dist(resultsMatrix)->resultsMatrix
	attr(resultsMatrix, "method") <- "dist"
	return(resultsMatrix) 
}

shared_dist <- dist.JSD(shared_file)

>>>>

# read in files
meta_file   <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF_metadata.txt'
shared_file <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF.an.unique_list.0.03.subsample.shared'
tax_file <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/mothur/gf_cdiff.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.an.unique_list.0.03.cons.taxonomy'
entero_list <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF.0.03.subsample.shared.for.0.03.dmm.5.mix.posterior'
entero_abund <- '~/Documents/Github/Schubert_humanCdGF_XXXX_2016/data/process/human_CdGF.0.03.subsample.shared.for.0.03.dmm.5.mix.relabund'

meta_file   <- read.table(meta_file, sep = '\t', header = T)
shared_file <- read.table(shared_file, sep='\t',header = T, row.names = 'Group')
tax_file <- read.table(tax_file, sep='\t',header = T, row.names = 'OTU')
entero_list <- read.table(entero_list, sep = '\t', header = T)
entero_abund <- read.table(entero_abund, sep = '\t', header = T)

# function to label otu with tax
source('~/Documents/Github/Schubert_humanCdGF_XXXX_2016/code/tax_level.R')

@@

# create enterotypes
entero_list <-
  unique(meta_file[meta_file$cage_id != 'inoculum',c('human_source','cage_id')])  
  gather(entero_list, 'Partition', 2:6)
